Assessing paravascular transport in the parenchyma by PDE constrained optimization.

### 2018-10-22 tex/paper.tex
update
more text

\begin{figure}
\centering
\includegraphics[width=0.70\textwidth]{T1function.png} 
\caption{Show the  function defined in \eqref{scaledmagnetization}. }
\label{figuredti} 
\end{figure}

@@

Below we will discuss the parameter identification and its sensitivity with respect to regularization parameters, noise and time-resolution. In presentation of the results, the relative error is defined as 
\begin{equation}
 X\sp{rel} = \frac{X_{found} -X_{true} }{ X_{true} }
\end{equation}
with $X$ as an arbitrary scalar control parameter. For the boundary parameter $g$, the relative error norm is defined as 
\begin{equation}
|| g ||\sp{rel}_{L\sp{2}(\Omega_1)} = \frac{ \sum\limits_t\sp{k}|| g_{found}(t) -g_{true}(t)||_{L(\Omega_1)} }{  \sum\limits_t\sp{k}||g_{true}(t)||_{L(\Omega_1)} }
\end{equation}
In the case that the minimization algorithm fails to converge within 1000 iteration will be indicated by a hyphen in Table~\ref{TAB::timesteps} Table~\ref{TAB::double}} and Table~\ref{Tab::Noise0.3}

@@

The convergence of the objective functional $F$ is influenced by the values of the regularization parameters $\alpha$ and $\beta$. Therefore the convergence was examined by a systematic study of the reconstruction of the manufactured solution with respect to a wide range of regularization parameters.

@@

In Tabel~\ref{Tab::Noise0.03}, we can see that a noise amplitude of 0.03, (10$\%$ of maximum initial condition) had negligible effect on the relative error. However, in Tabel~\ref{Tab::Noise0.3} the noise amplitude was increased to 0.3 (100$\%$ of maximum initial condition) and it is observed that for  $\alpha \leq 1.0e-4$  and $\beta \leq 1.0e-4$ the optimization failed to converge before reaching maximum iteration of 1000 steps. Furthermore, the relative boundary error $||g||\sp{rel}_{L\sp{2}(\Omega_1)}$ is larger for lower values of $\beta$.

@@

The results are shown in Tab.\ref{Tab::Real-data}, and the observations after 12 and 48 hours were compared with the corresponding states in Figure~\ref{Fig::realdata}. From Table~\ref{Tab::Real-data},it can be observed that $D_w$ have a higher value for $\alpha =1.0e-2$.

@@

\subsection*{Compare high DTI values with computed}
This gives a difference of $42 \%$ in grey matter and $ 100 \%$ in white matter compared to the estimated values using DTI.

@@

\section{Discussion}

The methodology presented here for identification of diffusion coefficients and boundary conditions with application to the glymphatic system appears to work quite 
well for regularization parameters varying by orders of magnitude. It is particularly interesting to see that the procedure efficiently removes noise as demonstrated
in the Figures \ref{12hourswithnoise} and \ref{24hourswithnoise} with noise levels of 30\% \kam{is this correctly stated}{\color{red} (0.3,-0.3) added to all values in range (0,g(t))}. 
Crucial in our application is the interplay between the regularization term that regulates the smoothness of the boundary conditions as well as
the integrate magnitude of the boundary conditions over time, i.e. $\alpha$ and $\beta$, and the
importance of interplay of these parameter increases with the number of time steps. This is, however, not surprising because our observations are sparse
in time and hence an oscillating boundary condition in time will minimized the integrated boundary condition at the cost of reducing the smoothness in time.

While a more comprehensive study involving more patients would be required in order to assess whether the clearance here happens faster than diffusion (\kam{egentlig er
vel dette det motsatte av clearance} a few remarks are in order. We find that the diffusion coefficients is XXX larger than what was found by the DTI modality.  
However, we have not yet been able to assessment the self-diffusion of water as well as the diffusivity of Gadovist used in this study in phantom models. As such 
the constants in equation XXX must be taken with caution. Furthermore,    
the computational model assumes isotropic diffusivity, but the anisotropy in the white matter is well documented, as shown by the FA in Fig\ref{figuredti}. It can be seen in Figure~\ref{Fig::realdata} that the region with high FA have negligible amounts of tracer present. Therefore it would seem that the anisotropy do not have direct impact on the computations, since the computation can not evaluate a static environment. Therefore  observation of tracer in regions with anisotropy can be considered a requirement for adding anisotropy to the model.
The regions with high diffusivity in Figure~\ref{figuredti},  have significant amount of diffusivity as seen in Figure~\ref{Fig::realdata}

@@

\section{Conclusion}

It can be concluded from the results that increasing the number of iterations gives rise to oscillations for poor regularizations parameters.

@@

>>>>

\begin{figure}
\centering
\includegraphics[width=0.70\textwidth]{T1function.png} 
\caption{Show the  function defined in \eqref{scaledmagnetization} with the white region indicating $T_1$ values for white matter,the grey region indicating $T_1$ values for grey matter,the blue region indicating $T_1$ values for CSF.  }
\label{figuredti} 
\end{figure}

@@

Below we will discuss the parameter identification and its sensitivity with respect to regularization parameters, noise and time-resolution. In presentation of the results, the relative error is defined as 
\begin{equation}
 X\sp{rel} = \frac{X_{found} -X_{true} }{ X_{true} }
\end{equation}
with $X$ as an arbitrary scalar control parameter. For the boundary parameter $g$, the relative error norm is defined as 
\begin{equation}
|| g ||\sp{rel}_{L\sp{2}(\Omega_1)} = \frac{ \sum\limits_t\sp{k}|| g_{found}(t) -g_{true}(t)||_{L(\Omega_1)} }{  \sum\limits_t\sp{k}||g_{true}(t)||_{L(\Omega_1)} }
\end{equation}
In the case that the minimization algorithm fails to converge within 1000 iteration will be indicated by a hyphen in Table~\ref{TAB::timesteps}, Table~\ref{TAB::double} and Table~\ref{Tab::Noise0.3}

@@

The convergence of the minimization is influenced by the values of the regularization parameters $\alpha$ and $\beta$. Therefore the convergence was examined by a systematic study of the reconstruction of the manufactured solution with respect to a wide range of regularization parameters.

@@

In Tabel~\ref{Tab::Noise0.03}, we can see that a noise amplitude of 0.03, (10$\%$ of maximum initial condition) had negligible effect on the relative error. Then in Tabel~\ref{Tab::Noise0.3} the noise amplitude was increased to 0.3 (100$\%$ of maximum initial condition), which gave a visible effect. The noise addition caused the number of iteration to increase, and in combination with more timesteps caused the optimization not to convergence for $\beta < 1.0$. Furthermore, the relative boundary error $||g||\sp{rel}_{L\sp{2}(\Omega_1)}$ is significantly larger for $\alpha< 1.0e-2 $ and $\beta < 1.0e-2$.

@@

The results are shown in Tab.\ref{Tab::Real-data}, and the observations after 12 and 48 hours were compared with the corresponding states in Figure~\ref{Fig::realdata}. From Table~\ref{Tab::Real-data},it can be observed that $D_w$ have 24\% higher value on average for $\alpha =1.0e-2$. It can also be observed that the $D_g$ have a consistent increases with a decreasing $\beta$.

@@

\subsection*{Compare high DTI values in white matter with computed}
This gives a difference of $42 \%$ in grey matter and $ 100 \%$ in white matter compared to the estimated values using DTI.

@@

\section{Discussion}
The methodology presented here for identification of diffusion coefficients and boundary conditions with application to the glymphatic system appears to work quite 
well for regularization parameters varying by orders of magnitude. The regularization parameters  $\alpha \in \lbrace 1.0e-6, 1.0e-2 \rbrace$, $\beta \in \lbrace 1.0e-2 , 1.0 \rbrace$ with the requirement $\alpha / \beta < 1.0e-2$ gave a relative error of  
4.1\% in grey matter and 3.6 \% in white matter. It is particularly interesting to see that the procedure efficiently removes noise as demonstrated
in the Figures \ref{12hourswithnoise} and \ref{24hourswithnoise} with noise amplitude of 23\% of maximum value. However, the addition of noise required that $\beta = 1.0 $ to obtain consistent convergence. 
Crucial in our application is the interplay between the regularization term that regulates the smoothness of the boundary conditions as well as
the integrate magnitude of the boundary conditions over time, i.e. $\alpha$ and $\beta$, and the
importance of interplay of these parameter increases with the number of time steps. This is, however, not surprising because our observations are sparse
in time and hence an oscillating boundary condition in time will minimized the integrated boundary condition at the cost of reducing the smoothness in time. The selected range of regularization parameters showed a decrease in error with more timesteps, rather than oscillation.

While a more comprehensive study involving more patients would be required in order to assess whether the clearance here happens faster than diffusion (\kam{egentlig er
vel dette det motsatte av clearance} a few remarks are in order. We find that the diffusion coefficients is 42-100\% larger than what was found by the DTI modality.  
However, we have not yet been able to assessment the self-diffusion of water as well as the diffusivity of Gadovist used in this study in phantom models. As such 
the constants in equation XXX must be taken with caution. Furthermore,    
the computational model assumes isotropic diffusivity, but the anisotropy in the white matter is well documented, as shown by the FA in Fig\ref{figuredti}. It can be seen in Figure~\ref{Fig::realdata} that the region with high FA have negligible amounts of tracer present. Therefore it would seem that the anisotropy do not have direct impact on the computations, since the computation can not evaluate a static environment. Therefore  observation of tracer in regions with anisotropy can be considered a requirement for adding anisotropy to the model.
The regions with high diffusivity in Figure~\ref{figuredti},  have significant amount of diffusivity as seen in Figure~\ref{Fig::realdata}

@@

%\section{Conclusion}

%It can be concluded from the results that increasing the number of iterations gives rise to oscillations for poor regularizations parameters.

@@

\clearpage
